\textsl{Position:} Is machine learning good or bad for the natural sciences?

### 2024-05-28 paper/main.tex
passes format checker

\twocolumn[
\icmltitle{\documentname: Is machine learning good or bad for the natural sciences?}

@@

\paragraph{Broader societal and ethical impacts:}
This \documentname{} is directly aimed at producing certain kinds of broader impacts, in the execution of natural-science investigations and projects.
ML has many roles in the natural sciences.
This work is intended to start a discussion which, in time, will support the implementation of ML in good roles in scientific projects, and criticize the implementation of ML in less good roles in scientific projects.
It is also intended to help practitioners understand and respond to biases introduced by the use of ML in those less-good roles.
The goal of this work is to improve the accuracy and success of the natural sciences.
However, if the recommendations in this \documentname{} are adopted by scientific communities, the costs of some scientific projects may increase.

@@

>>>>

\twocolumn[
\icmltitle{\textsl{Position:} Is machine learning good or bad for the natural sciences?}

@@

@@

\section*{Impact statement}
This \documentname{} is directly aimed at producing certain kinds of broader impacts, in the execution of natural-science investigations and projects.
ML has many roles in the natural sciences.
This work is intended to start a discussion which, in time, will support the implementation of ML in good roles in scientific projects, and criticize the implementation of ML in less good roles in scientific projects.
It is also intended to help practitioners understand and respond to biases introduced by the use of ML in those less-good roles.
The goal of this work is to improve the accuracy and success of the natural sciences.
However, if the recommendations in this \documentname{} are adopted by scientific communities, the costs of some scientific projects may increase.
